Designing and Developing a Personalised Recommender System

### 2021-02-11 paper/paper.tex
fleshed out introduction section of paper

\subsection{Domain of application}
The domain of this application is a recommender system for bars, using the Yelp dataset.
Decide whether I want to define the time-span for the date, 
depends on if there is too much data from all available time period.
I am also taking into accounts Covid-19 data when generating recommendations.

\subsection{Related work review}
Some related work

\subsection{Purpose/Aim}
The purpose of this application is to give suitable suggestions for a user to go to.
Using information about the user such as their location and personal preferences.

@@

\subsection{Data description}
The data I am using is taken from the Yelp dataset,
it includes user reviews of different businesses and services in a specific location.
There are 10 cities included in the dataset: Montreal, Calgary, Toronto, Pittsburgh, Charlotte, 
Urbana-Champaign, Phoenix, Las Vegas, Madison, and Cleveland. 
These user reviews include ratings, text feedback, and other such information.

@@

The program offers users opportunities to input information about themselves,
as well as make choices from a selection of items which the system provides or suggests.

\subsection{Recommendation algorithm}
What algorithm

\subsection{Output interface}
The output interface is the command line.
The system can output recommendations for bars which the user might like,
as well as information about how the system works and why certain suggestions were made,
at the user's request.

>>>>

\subsection{Domain of application}
The domain of this hybrid recommender system is restaurants, with a focus on trying new restaurants. 
This system is built around restaurants in a particular metropolitan area which serve a particular 
type of food.

\subsection{Related work review}
Hybrid recommender systems which combine Knowledge-based (KB) and Collaborative-filtering (CF) techniques 
are designed to combine the ability of KB techniques to give generic recommendations to new users with 
small profiles and the strength of CF to find peer users with unexpected shared preferences. 
This combination of techniques is particularly well suited to restaurants since a user may often be in the 
mood for a specific type of food, such as Italian or Chinese, so they only want to see suggestions of that 
type or restaurant, which is where the Knowledge-based recommender is helpful. 
A Collaborative-filtering algorithm will then be able to order all the restaurants which match this 
explicit criteria by how the user should rate them, based on the opinions of other similar users, 
helping them to discover new restaurants to try. 
These techniques are used in the Entree restaurant recommender system \cite{burke1999integrating,burke2000knowledge,burke2002hybrid,burke2007hybrid}. 
In particular, Burke's 1999 paper \cite{burke1999integrating} is the first to discuss specifically using these 
two techniques in the same cascaded style that I implement here.

\subsection{Purpose/Aim}
The purpose of this application is to give suitable suggestions of restaurants for a user to go to. 
The recommended restaurants should be in the metropolitan area which the user specifies, and serve the 
type of food that the user asks for. 
As well as fitting this explicit criteria, the suggested restaurants should be similar to other restaurants 
that the user has rated highly in the past and which other users with similar preferences also like. 
The system will allow the user to add ratings of the restaurants they are recommended, and these ratings will 
affect future suggestions the system gives for that user and other similar users.

@@

\subsection{Data description}
includes 10 metropolitan areas in the USA and Canada (20,565 restaurants) as well as given consideration 
to Covid-19 data when  which is included in the dataset. 
The data I am using is taken from the Yelp dataset,
it includes user reviews of different businesses and services in a specific location.
There are 10 cities included in the dataset: Montreal, Calgary, Toronto, Pittsburgh, Charlotte, 
Urbana-Champaign, Phoenix, Las Vegas, Madison, and Cleveland. 
These user reviews include ratings, text feedback, and other such information.

@@

\subsection{Recommendation algorithm}
I used a model-based approach to Collaborative Filtering based on matrix factorisation. 
The specific model is Single Value Decomposition (SVD), which was popularised by Simon Funk during the Netflix Prize. 
In my program, I fit the algorithm on a training set, and then for every restaurant of the specified category 
and in the specified city, I predict what the user would rate that restaurant. 
Then I sort those restaurants by their score and take the top 8 to present to the user.

\subsection{Output interface}
Recommendations and prediction scores are presented to the user via the command line interface and using an ASCII table. 
I used a python module called texttable for this, since it makes the output very clear and visually appealing. 
I chose to output the top 8 recommendations since I think this is enough variety and choice for the user to find 
a restaurant to try, without there being too many options which might overwhelm the user. 
If I presented more than 8 recommendations at a time, the table wouldn't fit in a single terminal output window and 
would require the user to scroll around to read different parts of the output. 
Since the user will be interacting with the system on a laptop or desktop computer through a command line interface, 
an ASCII table is the most visually attractive way to present information, and the white text on a (typically) black 
background will help accommodate users who are colourblind or who require a high-contrast interface. 
The interface is clear enough to understand that users of all ages are able to use the system, and if a user 
requires the text to be larger then they can increase the text size of their terminal. 
Along with the recommended restaurants, an explanation of how these results are calculated is also provided, as 
well as the prediction values themselves so the user can understand why they are being shown these suggestions. 
This, along with an option in the main menu to view information about the data the system uses and how it is used, 
further adds to the explainability and transparency.
